Chord: A Versatile Platform for Program Analysis

### 2011-04-12 main/doc/architecture.tex
updated documentation

\begin{center}
\texonly{\includegraphics[scale=0.7]{chord_arch.png}}
\htmlonly{{\htmlimg{chord_arch.png}}}
\end{center}

@@

The Java program to be analyzed is also specified via properties.
These properties are described in Section \ref{sec:program-props}.
Chord analyzes Java bytecode, not Java source code, and thus only requires
the program's class files.  Certain analyses, however, present
their results at the Java source code level, and thus require the program's
Java source files as well.

\subsubsection*{Java Program Representation}

@@

\subsubsection*{Computing Analysis Scope}

A pre-requisite to analyzing a Java program using any program analysis framework, including Chord, is
to compute the {\it analysis scope}: the set of methods of the program to be analyzed.  Chord implements
several standard scope construction algorithms from the literature that differ in aspects such as
scalability, precision, and usability for the problem at hand.  Chapter \ref{chap:computing-scope}
describes these algorithms in detail.

@@

Chord provides various {\it analysis templates}: classes containing boilerplate code that can be
extended by users to rapidly prototype different kinds of analyses.  An example is class RHSAnalysis,
named after [Reps, Horowitz, and Sagiv 1995], which can be extended by users to write a summary-based inter-procedural
context-sensitive static analysis by merely specifying the abstract domain and intra-procedural transfer functions.
Another exampls is DynamicAnalysis, which can be extended by
users to write a dynamic analysis by merely specifying which of various provided events to instrument, and
the transfer functions for those events.

A distinctive aspect of Chord is that each analysis is written modularly, independent of other analyses, along with lightweight
annotations specifying the inputs and outputs of the analysis.
Users must provide a unique name to each analysis, which allows the desired analyses to be called from the
command-line, via a property named \code{chord.run.analyses}.
Chord's runtime automatically computes
producer-consumer relationships between analyses (e.g., determines which analysis produces as output a
result that is needed as input by another analysis).  Before running a desired analysis,
Chord recursively runs other analyses until the inputs to the desired analysis have been computed; it
finally runs the desired analysis to produce the outputs of that analysis.

Chord can be invoked in one of two modes: classic or modern (depending upon whether the value of property
\code{chord.classic} is \code{true} (default) or \code{false}, respectively).
These two modes defer in the semantics of dependencies between analyses.  In particular, the classic mode
is simpler to understand for novice users (the dependencies are only data dependencies) but has a sequential
runtime, whereas the modern mode is harder to understand (there are both data and control dependencies)
but has a parallel runtime that is capable of running analyses without dependencies between
them in parallel.  The parallel runtime is based on \xlink{Habanero-Java}{http://habanero.rice.edu/hj.html},
and the semantics of the dependencies between analyses is based on the
\xlink{Habanero Concurrent Collections (CnC)}{http://habanero.rice.edu/cnc.html} declarative parallel
programming model.

Chapter \ref{chap:analyses} describes the various analysis templates and how to connect disparate analyses
together via dependencies in either of the above two modes.

@@

>>>>

\begin{center}
\includeimage{0.7}{chord_arch.png}
%\texonly{\includegraphics[scale=0.7]{chord_arch.png}}
%\htmlonly{{\htmlimg{chord_arch.png}}}
\end{center}

@@

The Java program to be analyzed is also specified via properties.
%These properties are described in Section \ref{sec:program-props}.
Chapter \ref{chap:program-setup} describes how to setup a Java program for analysis using Chord.
Chord analyzes Java bytecode, not Java source code, and thus only requires
the program's class files.  Certain analyses, however, present
their results at the Java source code level, and thus require the program's
Java source files as well.

\subsubsection*{Program Representation}

@@

\subsubsection*{Analysis Scope Construction}

A pre-requisite to analyzing a Java program using any program analysis framework, including Chord, is
to compute the {\it analysis scope}: which parts of the program to analyze.  Chord implements
several standard scope construction algorithms from the literature that differ in aspects such as
scalability, precision, and usability for the problem at hand.  Chapter \ref{chap:computing-scope}
describes these algorithms in detail.

@@

A distinctive aspect of Chord is that each analysis is written modularly, independent of other analyses, along with lightweight
annotations specifying the inputs and outputs of the analysis.
Chord's runtime automatically computes
dependencies between analyses (e.g., determines which analysis produces as output a
result that is needed as input by another analysis).  Before running a desired analysis,
Chord recursively runs other analyses until the inputs to the desired analysis have been computed; it
finally runs the desired analysis to produce the outputs of that analysis.

Chord can be invoked in one of two modes: classic or modern.
These two modes defer in the semantics of dependencies between analyses.  In particular, the classic mode
is simpler to understand for novice users (the dependencies are only data dependencies) but has a sequential
runtime, whereas the modern mode is harder to understand (there are both data and control dependencies)
but has a parallel runtime that is capable of running analyses without dependencies between
them in parallel.  The parallel runtime is based on \xlink{Habanero-Java}{http://habanero.rice.edu/hj.html},
and the semantics of the dependencies between analyses is based on the
\xlink{Habanero Concurrent Collections (CnC)}{http://habanero.rice.edu/cnc.html} declarative parallel
programming model.

Chapter \ref{chap:project} describes how to write and run analyses in Chord.

\subsubsection*{Analysis Templates}

Chord provides various {\it analysis templates}: classes containing boilerplate code that can be
extended by users to rapidly prototype different kinds of analyses.  An example is class RHSAnalysis,
named after [Reps, Horowitz, and Sagiv 1995], which can be extended by users to write a summary-based inter-procedural
context-sensitive static analysis by merely specifying the abstract domain and intra-procedural transfer functions.
Another example is DynamicAnalysis, which can be extended by
users to write a dynamic analysis by merely specifying which of various provided events to instrument, and
the transfer functions for those events.
Chapter \ref{chap:analysis-templates} describes the various analysis templates.

@@

\subsubsection*{Predefined Analyses}

Chapter \ref{chap:predefined-analyses} describes many standard analyses that are implemented in Chord.

### 2011-04-12 main/doc/datalog_analysis.tex
updated documentation

A common way to rapidly prototype program analyses in Chord is using a declarative
logic-programming language called Datalog.  This chapter describes all aspects of
Datalog analysis in Chord.
Section \ref{sec:writing-datalog-analysis} explains how to write a Datalog analysis,
Section \ref{sec:running-datalog-analysis} explains how to run it, and
Section \ref{sec:tuning-datalog-analysis} explains how to tune its performance.
Finally, Section \ref{sec:bdd} explains the representation of BDDs (Binary Decision Diagrams)
which are a data structure central to executing Datalog analyses.

@@

A Datalog analysis declares a bunch of input/output program relations,
each over one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.
An example of such an analysis is shown below:

@@

Any line that begins with a {\tt \#} is regarded a comment, except a
line of the form ``{\tt \#} {\tt name=<...>}", which specifies the name
{\tt <...>} of the Datalog analysis.
Each Datalog analysis is expected to have exactly one such line.
The above Datalog analysis is named {\tt datarace-dlog}.
In Chord, all Datalog analysis names have suffix
{\tt -dlog} and all Java analysis names have suffix {\tt -java}, but
this is merely a convention that analysis writers are free to deviate from.
The name of each analysis, written in Datalog or in Java, is expected to be
unique across all analyses in scope (i.e., across all analyses in paths
specified by properties \code{chord.dlog.analysis.path} and \code{chord.java.analysis.path}).

The {\tt .include "<...>.dom"} lines specify each program domain named
{\tt <...>} that is needed by the Datalog analysis, i.e., each domain over which
any program relation that is input/output by the Datalog analysis is defined. 
The declaration of each such relation specifies the domain of each of the relation's attributes.
If the same domain appears in multiple attributes of a relation then
contiguous integers starting from 0 must be used to distinguish them; for instance,
in the above example, {\tt candidate} is a binary relation, both of whose
attributes have domain E, and they are distinguished as E0 and E1.

Each relation is represented symbolically (as opposed to explicitly)
using a graph-based data structure called a Binary Decision Diagram (BDD for short).
Each domain containing N elements is assigned log2(N) BDD variables.
The size of a BDD and the efficiency of operations on it depends heavily
on the order of these BDD variables.
The {\tt .bddvarorder <...>} line in the Datalog analysis enables the Datalog
analysis writer to specify this order.
It must list all domains along with their numerical suffixes, separated
by {\tt \_} or {\tt x}.
Using a {\tt \_} between two domains, such as {\tt T0\_T1}, means that the BDD variables assigned
to domain {\tt T0} precede those assigned to domain {\tt T1} in the BDD variable
order for this Datalog analysis.
Using a {\tt x} between two domains, such as {\tt E0xE1}, means that the
BDD variables assigned to domains {\tt E0} and {\tt E1}
will be interleaved in the BDD variable order for this Datalog analysis.
See Section \ref{sec:bdd} for more details on BDD representations.

Each Datalog analysis rule is a Horn clause of the form
{\tt R(t) :- R1(t1), ..., Rn(tn)}
meaning that if relations {\tt R1}, ..., {\tt Rn} contain tuples {\tt t1}, ..., {\tt tn}
respectively, then relation {\tt R} contains tuple {\tt t}.
A backslash may be used at the end of a line to break long rules for readability.
The Datalog analysis solver bddbddb used in Chord does not apply any
sophisticated optimizations to simplify the rules; besides the BDD variable order,
the manner in which these rules are expressed heavily affects the performance of
the solver.  For instance, an important manual optimization involves breaking down
long rules into multiple shorter rules communicating via intermediate relations.
See Section \ref{sec:tuning-datalog-analysis} for hints on tuning the performance
of Datalog analyses.

\section{Running a Datalog Analysis}
\label{sec:running-datalog-analysis}

Chord interprets each file with extension {\tt .dlog} or {\tt .datalog} in the path specified by
property \code{chord.dlog.analysis.path} as a program analysis expressed in Datalog.

{\bf Under Construction}

\section{Tuning a Datalog Analysis}
\label{sec:tuning-datalog-analysis}

@@

\begin{framed}
\begin{verbatim}
ant -Ddlog.file=<file> -Dwork.dir=<dir> solve
\end{verbatim}
\end{framed}

where {\tt <file>} denotes the file defining the Datalog analysis
to be tuned, and {\tt <dir>} is the directory containing the
program domains ({\tt *.dom} files) and program relations ({\tt *.bdd} files)
consumed by the analysis (this is by default the
\code{chord_output/bddbddb/} directory generated
by a previous run of Chord.

\begin{enumerate}
\item
Set properties \verb+noisy=yes+, \verb+tracesolve=yes+, and \verb+fulltracesolve=yes+
on the above command line and observe which rule gets ``stuck" (i.e., takes several seconds to solve).
\verb+fulltracesolve+ is seldom useful, but \verb+noisy+ and \verb+tracesolve+ are
often very useful.  Once you identify the rule that is getting stuck, it
will also tell you which relations and which domains used in that rule,
and which operation on them, is taking a long time to solve.  Then try
to fix the problem with that rule by doing either or both of the following:
\begin{itemize}
\item
Break down the rule into multiple rules by creating intermediate relations (the more
relations you have on the RHS of a rule the slower it generally takes to solve
that rule).
\item
Change the relative order of the domains of those
relations in the BDD variable order
(note that you can use either `\_' or `x' between a pair of domains).
\end{itemize}

\item
Once you have ensured that none of the rules is getting ``stuck",
you will notice that some rules are applied too many times, and so
although each application of the rule itself isn't taking too much
time, the cumulative time for the rule is too much.  After finishing
solving a Datalog analysis, bddbddb prints how long each rule took to
solve (both in terms of the number of times it was applied and the
cumulative time it took).  It sorts the rules in the order of the
cumulative time.  You need to focus on the rules that took the most
time to solve (they will be at the bottom of the list).  Assuming you
removed the problem of rules getting ``stuck", the rules will roughly
be in the order of the number of times they were applied.  Here is an
example:

@@

\item
You can add the \verb+.split+ keyword at the end of certain rules as a
hint to bddbddb to decompose those rules into simpler ones that can be
solved faster.  You can also set property \verb+split_all_rules=yes+ as shorthand
for splitting all rules without adding the \verb+.split+ keyword to any of
them, though I seldom find splitting all rules helpful.

\item
You can try to decompose a single Datalog analysis file into two separate Datalog analysis
files.  Of course, you cannot separate mutually-recursive rules into two
different analyses, but if you unnecessarily club
together rules that could have gone into different analyses, then they
can put conflicting demands on bddbddb (e.g., on the BDD variable order).
So if rule 2 uses the result of rule 1 and rule 1 does not use the result of
rule 2, then put rule 1 and rule 2 in separate Datalog analyses.

\item
Observe the sizes of the BDDs representing the relations that are
input and output.  bddbddb prints both the number of tuples in each
relation and the number of nodes in the BDD.  Try changing the
BDD variable order for the domains of the relation, and observe how the
number of nodes in the BDD for that relation change.  You will
notice that some orders perform remarkably better than others.  Then
note down these orders as invariants that you will not violate as
you tweak other things.

\item
The relative order of values *within* domains (e.g.,
in domains named \verb+M+, \verb+H+, \verb+C+, etc. in Chord) affects the
performance of bddbddb, but
I've never tried changing this and studying its effect.  It might be
worth trying.  For instance, John Whaley's PLDI'04 paper describes a
specific way in which he numbers contexts (in domain \verb+C+) and that it was
fundamental to the speedup of his ``infinity"-CFA points-to analysis.

\item
Finally, it is worth emphasizing that BDDs are not magic.
If your algorithm itself is fundamentally hard to scale, then BDDs are
unlikely to help you a whole lot.  Secondly, many things are awkward to
encode as integers (e.g., the abstract contexts in domain \verb+C+ 
in Chord) or as Datalog rules.
For instance, I've noticed that summary-based context-sensitive program
analyses are hard to express in Datalog.  The may-happen-in-parallel
analysis provided in Chord shows a relatively simple kind of summary-based
analysis that uses the Reps-Horwitz-Sagiv tabulation algorithm.  But this
is as far as I could get---more complicated summary-based algorithms are
best written in Java itself instead of Datalog.
\end{enumerate}

@@

If two domains are uninterleaved in the declared domain order in a Datalog program (i.e., {\tt \_} is used instead of {\tt x} between them),
then the BDD variables assigned to those domains are ordered in reverse order in the underlying BDD factory.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0\_Z0} is (in level2var format)
``70,69,68,67,66,65,64,63,108,107,106,105".

If two domains are interleaved in the declared domain order in a Datalog program (i.e., {\tt x} is used instead of {\tt \_} between them),
then the BDD variables assigned to those domains are still ordered in reverse order of IDs in the underlying BDD factory,
but they are also interleaved.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0xZ0} is (in level2var format)
``70,108,69,107,68,106,67,105,66,65,64,63".

>>>>

A common way to rapidly prototype analyses in Chord is using a declarative
logic-programming language called Datalog.  This chapter describes all aspects of
Datalog analyses in Chord.
Section \ref{sec:writing-datalog-analysis} explains how to write and run a Datalog analysis.
Section \ref{sec:tuning-datalog-analysis} explains how to tune its performance.
Finally, Section \ref{sec:bdd} explains the representation of BDDs (Binary Decision Diagrams)
which are a data structure central to executing Datalog analyses.

@@

A Datalog analysis declares a bunch of input/output program relations,
each over one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.
It can be defined in any file with extension {\tt .dlog}
in any directory in the path specified by property \code{chord.dlog.analysis.path}.
An example Datalog analysis is shown below:

@@

Any line that begins with a ``{\tt \#}" is regarded a comment, except a
line of the form ``\code{# name=<ANALYSIS_NAME>}'', which specifies the name
\code{<ANALYSIS_NAME>} of the Datalog analysis.
Each Datalog analysis is expected to have exactly one such line.
The above Datalog analysis is named {\tt datarace-dlog}.

The ``\code{.include "<DOM_NAME>.dom"}'' lines specify each program domain named
\code{<DOM_NAME>} that is needed by the Datalog analysis, i.e., each domain over which
any program relation that is input/output by the Datalog analysis is defined. 
The declaration of each such relation specifies the domain of each of the relation's attributes.
If the same domain appears in multiple attributes of a relation then
contiguous integers starting from 0 must be used to distinguish them; for instance,
in the above example, {\tt candidate} is a binary relation, both of whose
attributes have domain {\tt E}, and they are distinguished as {\tt E0} and {\tt E1}.

Each relation is represented symbolically (as opposed to explicitly)
using a graph-based data structure called a Binary Decision Diagram (BDD for short).
Each domain containing N elements is assigned log2(N) BDD variables.
The size of a BDD and the efficiency of operations on it depends heavily
on the order of these BDD variables.
The ``\code{.bddvarorder <BDD_VAR_ORDER>}'' line in the Datalog analysis enables the Datalog
analysis writer to specify this order.
It must list all domains along with their numerical suffixes, separated
by `{\tt \_}' or `{\tt x}'.
Using a `{\tt \_}' between two domains, such as {\tt T0\_T1}, means that the BDD variables assigned
to domain {\tt T0} precede those assigned to domain {\tt T1} in the BDD variable
order for this Datalog analysis.
Using a `{\tt x}' between two domains, such as {\tt E0xE1}, means that the
BDD variables assigned to domains {\tt E0} and {\tt E1}
will be interleaved in the BDD variable order for this Datalog analysis.
See Section \ref{sec:bdd} for more details on BDD representations.

Each Datalog analysis rule is a Horn clause of the form
``{\tt R(t) :- R1(t1), ..., Rn(tn)}"
meaning that if relations {\tt R1}, ..., {\tt Rn} contain tuples {\tt t1}, ..., {\tt tn}
respectively, then relation {\tt R} contains tuple {\tt t}.
A backslash may be used at the end of a line to break long rules for readability.
The Datalog analysis solver bddbddb used in Chord does not apply any
sophisticated optimizations to simplify the rules; besides the BDD variable order,
the manner in which these rules are expressed heavily affects the performance of
the solver.  For instance, an important manual optimization involves breaking down
long rules into multiple shorter rules communicating via intermediate relations.
See Section \ref{sec:tuning-datalog-analysis} for hints on tuning the performance
of Datalog analyses.

Running a Datalog analysis is no different from running any other kind of analysis
in Chord.  See Chapter \ref{chap:running-analysis} for how to run an analysis.

\section{Tuning Performance}
\label{sec:tuning-datalog-analysis}

@@

\begin{framed}
\begin{verbatim}
ant -Ddlog.file=<FILE> -Dwork.dir=<DIR> solve
\end{verbatim}
\end{framed}

where {\tt <FILE>} is the file defining the Datalog analysis
to be tuned, and {\tt <DIR>} is the directory containing the
program domains ({\tt *.dom} files) and program relations ({\tt *.bdd} files)
consumed by the analysis (this is by default the
\code{chord_output/bddbddb/} directory generated
by a previous run of Chord.

\begin{enumerate}

\item

Set properties \verb+noisy=yes+, \verb+tracesolve=yes+, and \verb+fulltracesolve=yes+
on the above command line and observe which rule gets ``stuck" (i.e., takes several seconds to solve).
\verb+fulltracesolve+ is seldom useful, but \verb+noisy+ and \verb+tracesolve+ are
often very useful.  Once you identify the rule that is getting stuck, it
will also tell you which relations and which domains used in that rule,
and which operation on them, is taking a long time to solve.  Then try
to fix the problem with that rule by doing either or both of the following:
\begin{itemize}
\item
Break down the rule into multiple rules by creating intermediate relations (the more
relations you have on the RHS of a rule the slower it generally takes to solve
that rule).
\item
Change the relative order of the domains of those
relations in the BDD variable order
(note that you can use either `\_' or `x' between a pair of domains).
\end{itemize}

\item

Once you have ensured that none of the rules is getting ``stuck",
you will notice that some rules are applied too many times, and so
although each application of the rule itself isn't taking too much
time, the cumulative time for the rule is too much.  After finishing
solving a Datalog analysis, bddbddb prints how long each rule took to
solve (both in terms of the number of times it was applied and the
cumulative time it took).  It sorts the rules in the order of the
cumulative time.  You need to focus on the rules that took the most
time to solve (they will be at the bottom of the list).  Assuming you
removed the problem of rules getting ``stuck", the rules will roughly
be in the order of the number of times they were applied.  Here is an
example:

@@

\item

You can add the \verb+.split+ keyword at the end of certain rules as a
hint to bddbddb to decompose those rules into simpler ones that can be
solved faster.  You can also set property \verb+split_all_rules=yes+ as shorthand
for splitting all rules without adding the \verb+.split+ keyword to any of
them, though I seldom find splitting all rules helpful.

\item

You can try to decompose a single Datalog analysis file into two separate Datalog analysis
files.  Of course, you cannot separate mutually-recursive rules into two
different analyses, but if you unnecessarily club
together rules that could have gone into different analyses, then they
can put conflicting demands on bddbddb (e.g., on the BDD variable order).
So if rule 2 uses the result of rule 1 and rule 1 does not use the result of
rule 2, then put rule 1 and rule 2 in separate Datalog analyses.

\item

Observe the sizes of the BDDs representing the relations that are
input and output.  bddbddb prints both the number of tuples in each
relation and the number of nodes in the BDD.  Try changing the
BDD variable order for the domains of the relation, and observe how the
number of nodes in the BDD for that relation change.  You will
notice that some orders perform remarkably better than others.  Then
note down these orders as invariants that you will not violate as
you tweak other things.

\item

The relative order of values *within* domains (e.g.,
in domains named \verb+M+, \verb+H+, \verb+C+, etc. in Chord) affects the
performance of bddbddb, but
I've never tried changing this and studying its effect.  It might be
worth trying.  For instance, John Whaley's PLDI'04 paper describes a
specific way in which he numbers contexts (in domain \verb+C+) and that it was
fundamental to the speedup of his ``infinity"-CFA points-to analysis.

\item

Finally, it is worth emphasizing that BDDs are not magic.
If your algorithm itself is fundamentally hard to scale, then BDDs are
unlikely to help you a whole lot.  Secondly, many things are awkward to
encode as integers (e.g., the abstract contexts in domain \verb+C+ 
in Chord) or as Datalog rules.
For instance, I've noticed that summary-based context-sensitive program
analyses are hard to express in Datalog.  The may-happen-in-parallel
analysis provided in Chord shows a relatively simple kind of summary-based
analysis that uses the Reps-Horwitz-Sagiv tabulation algorithm.  But this
is as far as I could get---more complicated summary-based algorithms are
best written in Java itself instead of Datalog.
\end{enumerate}

@@

If two domains are uninterleaved in the declared domain order in a Datalog program (i.e., `{\tt \_}' is used instead of `{\tt x}' between them),
then the BDD variables assigned to those domains are ordered in reverse order in the underlying BDD factory.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0\_Z0} is (in level2var format)
``70,69,68,67,66,65,64,63,108,107,106,105".

If two domains are interleaved in the declared domain order in a Datalog program (i.e., `{\tt x}' is used instead of `{\tt \_}' between them),
then the BDD variables assigned to those domains are still ordered in reverse order of IDs in the underlying BDD factory,
but they are also interleaved.
For instance, the BDD variable order corresponding to the declared domain order {\tt F0xZ0} is (in level2var format)
``70,108,69,107,68,106,67,105,66,65,64,63".

### 2011-04-12 main/doc/predefined_analyses.tex
updated documentation

To run this analysis, run the following command in Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<...> -Dchord.run.analyses=cipa-0cfa-dlog run
\end{verbatim}
\end{framed}

@@

To run Chord's static datarace analysis, run the following
command in Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<...> -Dchord.run.analyses=datarace-java run
\end{verbatim}
\end{framed}

where {\tt <...>} denotes the absolute or relative path of a directory
containing a file named \code{chord.properties} which defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path}.  See Section \ref{sec:program-props} for the
meaning of these properties.

Directory \code{examples/datarace_test/} in Chord's main directory provides a toy Java
program on which one can run the datarace analysis.  First run {\tt
  ant} in that directory (in order to compile the program's {\tt
  .java} files to {\tt .class} files) and then run the above command
in Chord's main directory with {\tt <...>} replaced by
\code{examples/datarace_test/}.  Upon successful completion, the
following files should be produced in directory
\code{examples/datarace_test/chord_output/}:

@@

To run Chord's static deadlock analysis,  run the following
command in Chord's main directory:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<...> -Dchord.run.analyses=deadlock-java run
\end{verbatim}
\end{framed}

where {\tt <...>} denotes the absolute or relative path of a directory
containing a file named \code{chord.properties} which defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path}.  See Section \ref{sec:program-props} for the
meaning of these properties.

Directory \code{examples/deadlock_test/} in Chord's main directory provides a toy Java
program on which one can run the deadlock analysis.  First run {\tt
  ant} in that directory (in order to compile the program's {\tt
  .java} files to {\tt .class} files) and then run the above command
in Chord's main directory with {\tt <...>} replaced by
\code{examples/deadlock_test/}.  Upon successful completion, the
file \code{deadlocks.html} should be produced in directory
\code{examples/deadlock_test/chord_output/}.

>>>>

To run this analysis, run the following command:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<WORK_DIR> -Dchord.run.analyses=cipa-0cfa-dlog run
\end{verbatim}
\end{framed}

where \code{<WORK_DIR>} is a directory
containing a file named \code{chord.properties} that defines
properties \code{chord.main.class} and \code{chord.class.path} specifying
the main class and the application classpath, respectively, of the program
to be analyzed.

@@

To run Chord's static datarace analysis, run the following command:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<WORK_DIR> -Dchord.run.analyses=datarace-java run
\end{verbatim}
\end{framed}

where \code{<WORK_DIR>} is a directory
containing a file named \code{chord.properties} that defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path} specifying the main class, the application classpath, and
the Java source path, respectively, of the program to be analyzed.

Directory \code{<CHORD_MAIN_DIR>/examples/datarace_test/} provides a toy Java
program on which one can run the datarace analysis.  First run {\tt ant} in that
directory (in order to compile the program's {\tt .java} files to {\tt .class}
files) and then run the above command with \code{<WORK_DIR>} replaced by
\code{examples/datarace_test/}.  Upon successful completion, the
following files should be produced in directory
\code{examples/datarace_test/chord_output/}:

@@

To run Chord's static deadlock analysis,  run the following command:

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<WORK_DIR> -Dchord.run.analyses=deadlock-java run
\end{verbatim}
\end{framed}

where \code{<WORK_DIR>} is a directory
containing a file named \code{chord.properties} that defines
properties \code{chord.main.class}, \code{chord.class.path}, and
\code{chord.src.path} specifying the main class, the application classpath,
and the Java source path, respectively, of the program to be analyzed.

Directory \code{<CHORD_MAIN_DIR>/examples/deadlock_test/} provides a toy Java
program on which one can run the deadlock analysis.  First run {\tt ant} in that
directory (in order to compile the program's {\tt .java} files to {\tt .class}
files) and then run the above command with \code{<WORK_DIR>} replaced by
\code{examples/deadlock_test/}.  Upon successful completion, the
file \code{deadlocks.html} should be produced in directory
\code{examples/deadlock_test/chord_output/}.
